Inferring the existence and direction of causal associations in the face of measurement error

### 2017-01-26 docs/manuscript.Rmd

>>>>

Genetic associations have the desirable property of ensuring the causal direction is from genotype to trait. Mediation based approaches such as the causal inference test (CIT) use this property to infer the causal direction between two traits, while Mendelian randomization uses the property to estimate the causal effect size if knowledge of the

 by evaluating if the genetic association on the consequential trait is abbrogated by adjusting for the causal trait. Mendelian randomization, by contrast assumes a priori knowledge of which of the two traits the genetic variant is acting on primarily, and then creates a proxy to estimate its causal effect on
